\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-09 paper/main.tex
paper: added query schematic for basic plans
paper: keep refining algorithm section
paper: added description of cdc data to paper, along with queries

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[activate={true,nocompatibility},final,kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[style=ieee]{biblatex}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{hyperref} % load after other packages
\addbibresource{references.bib}

>>>>

\documentclass{vldb}
\usepackage{balance}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[activate={true,nocompatibility},final,kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}
\usepackage[subtle]{savetrees}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[style=numeric,firstinits=true]{biblatex}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{hyperref} % load after other packages
\usepackage{graphicx} % includegraphics
\usepackage{listings} % code samples with syntax hl
\usepackage{qtree} % for simple tree diagrams
\usepackage{subcaption}
\addbibresource{references.bib}

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

% listings settings
\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}; should come as last argument
  basicstyle=\ttfamily\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{red},    % comment style
  %frame=single,	                   % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
%  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
%  numberstyle=\tiny\color{gray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
%  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mauve},     % string literal style
  tabsize=2,	                   % sets default tabsize to 2 spaces
}

### 2017-02-09 paper/queries.tex
paper: added description of cdc data to paper, along with queries

\begin{tabular}{ll}
\toprule
\# & Query \\
\midrule
0 & \verb|SELECT BLD FROM acs;| \label{q0} \\
1 & \verb|SELECT BLD as units_in_structure, COUNT(ST) as estimate FROM acs GROUP BY BLD;| \label{q1} \\
2 & \verb|SELECT BATH as has_bath, COUNT(ST) as ct FROM acs GROUP BY BATH;| \label{q2} \\
3 & \verb|SELECT ACR as lotsize, AVG(BDSP) as avg_num_bedrooms FROM acs GROUP BY ACR;| \label{q3} \\
4 & \verb|SELECT PSF as has_sub_families, SUM(NP) as num_people FROM acs GROUP BY PSF;| \label{q4} \\
5 & \verb|SELECT AVG(NP) as avg_num_people FROM acs;| \label{q5} \\
6 & \verb|SELECT BDSP as num_bedrooms, AVG(ACR) as avg_lot_size FROM acs WHERE VEH >= 2 GROUP BY BDSP;| \label{q6} \\
\bottomrule
\end{tabular}

>>>>

\newcounter{queryno}
\begin{tabular}{cl}
\toprule
\# & \multicolumn{1}{c}{Query} \\
\midrule
1 & \verb|SELECT income, AVG(weight) FROM demo, exams WHERE demo.id = exams.id id GROUP BY income;| \refstepcounter{queryno} \label{q1} \\
2 & 
\begin{minipage}{6in}
\begin{lstlisting}[breaklines]
SELECT income, COUNT(*), AVG(cholesterol) 
FROM demo, exams, labs WHERE demos.id = exams.id AND exams.id = labs.id AND
income = 15 OR income = 13 AND weight >= 63 GROUP BY income;
\end{lstlisting}
\end{minipage}
\refstepcounter{queryno} \label{q2} \\
3 & \verb|SELECT MAX(blood_lead) FROM exams, labs WHERE exams.id = labs.id AND waist_circumference >= 87;| \refstepcounter{queryno} \label{q3} \\
% 1 & \verb|SELECT BLD FROM acs;| \refstepcounter{queryno} \label{q1} \\
% 2 & \verb|SELECT BLD as units_in_structure, COUNT(ST) as estimate FROM acs GROUP BY BLD;| \refstepcounter{queryno} \label{q2} \\
% 3 & \verb|SELECT BATH as has_bath, COUNT(ST) as ct FROM acs GROUP BY BATH;| \refstepcounter{queryno} \label{q3} \\
% 4 & \verb|SELECT ACR as lotsize, AVG(BDSP) as avg_num_bedrooms FROM acs GROUP BY ACR;| \refstepcounter{queryno} \label{q4} \\
% 5 & \verb|SELECT PSF as has_sub_families, SUM(NP) as num_people FROM acs GROUP BY PSF;| \refstepcounter{queryno} \label{q5} \\
% 6 & \verb|SELECT AVG(NP) as avg_num_people FROM acs;| \refstepcounter{queryno} \label{q6} \\
% 7 & \verb|SELECT BDSP as num_bedrooms, AVG(ACR) as avg_lot_size FROM acs WHERE VEH >= 2 GROUP BY BDSP;| \refstepcounter{queryno} \label{q7} \\
% 8 & \verb|SELECT MIN(RMSP) as min_num_rooms FROM acs WHERE RWAT=2;| \refstepcounter{queryno} \label{q8} \\
% 9 & \verb|SELECT * FROM dirty m where m.f1 >= 2;| \refstepcounter{queryno} \label{q9} \\
% 10 & \verb|SELECT * FROM dirty where dirty.f1 <= 2;| \refstepcounter{queryno} \label{q10} \\
% 11 & \verb|SELECT MAX(f2) as max_f2 FROM dirty GROUP BY dirty.f1;| \refstepcounter{queryno} \label{q11} \\
% 12 & \verb|SELECT m1.f1, m1.f2 FROM dirty m1, clean m2 WHERE m1.f1 = m2.f1 and m1.f1 = 1 and m2.f2 = 69;| \refstepcounter{queryno} \label{q12} \\
% 13 & \verb|SELECT d1.f1 FROM dirty d1, clean d2 WHERE d1.f1 = d2.f1 and d2.f2 = 50;| \refstepcounter{queryno} \label{q13} \\
\bottomrule
\end{tabular}
